Predicting Which States are Most Interested in the term *China Virus* Based off Identity Politics, Demography and COVID-19 Statistics 

### 2020-05-04 Final-Draft.Rmd
cahnges

## 3.1 Markov Chain Algorithm

## 3.2 Models of Interest

## 3.3 Model Descriptions

@@

# 4. Model Evaluation

## 4.1 Model 1 Evaluation( Repeated measures)

>>>>

## Model 1 Repeated Measures Model

  For our simplest model we decided to use a repeated measures model. Our team decided that the repeated measures model was necessary component because of how our data is set up. As we can see in our dataset, each state has a value for their `ChinaVirusInterest` for each day in our target period (2020-03-14 - 2020-03-21). Given the ability to use repeated measures and our prior understanding of the varying characteristics (demographic,political,covid-impact) within different states, the repeated measures model allows us to capture these differences in `ChinaVirusInterest` with the $\theta_i$ value which represents each state's mean value.

### Model Structure

$$\begin{aligned}
Y_{ij}|\theta_i, \mu, \sigma_w, \sigma_b \sim N(\theta_i,\sigma_w^2)\\
\theta_i|\mu,\sigma_b \overset{ind}{\sim} N(\mu, \sigma_b^2)\\
\sigma_b,\sigma_w \sim Exp(...)
\end{aligned}$$

$Y_{ij} = $ `ChinaVirusInterest` per $i=State$, and $j= Day$
$\theta_i = $ State i's unique mean value
$\sigma_w = $ within state variation
$\sigma_b = $ between state variation

```{r}
model_data<-
  Finaldata%>%
  mutate(Day=as.numeric(Day)-as.numeric(min(Day)))%>%
  select(ChinaVirusInterest, Day, percent_white, StateColor, positive, State)

model_data<- na.omit(model_data)
```

```{r}
#Repeated Measures Model
set.seed(454)
RM_model <- stan_glmer(
  ChinaVirusInterest ~ (1 | State),
  data = model_data, family = gaussian,
)
```

### 3.2 Model Descriptions

@@

# 4. Model Evaluation (RESULTS)

## 4.1 Model 1 Evaluation (Repeated measures)
